The Iterative Signature Algorithm for Gene Expression Data

### 2012-09-22 eisa/inst/doc/EISA_tutorial.Rnw
Removed the unneeded loading of the 'affy' package in an eisa vignette.

In this tutorial we will use the data in the \Rpackage{ALL}
package. 
<<load the data,cache=FALSE>>=
library(ALL)
library(hgu95av2.db)
library(affy)
data(ALL)
@
This is a data set from a clinical trial in acute
lymphoblastic leukemia and it contains \Sexpr{ncol(ALL)} samples
altogether.

>>>>

In this tutorial we will use the data in the \Rpackage{ALL}
package. 
<<load the data,cache=FALSE>>=
library(ALL)
library(hgu95av2.db)
data(ALL)
@
This is a data set from a clinical trial in acute
lymphoblastic leukemia and it contains \Sexpr{ncol(ALL)} samples
altogether.
